\begin{problem}{25}

  The tribe of \emph{Supmuw} considers being eaten by a wumpus to be Nirvana,
  the highest obtainable state of existence.  (Being eaten by the wumpus gives
  about the same experience as listening to grunge music.)
  If the wumpus is in the same location as a pit, then the adventurer would
  fall into the pit before being eaten.
  The adventurer must be sure that the wumpus isn't with a pit before walking
  into the wumpus' location.  Nirvana is only reached if the agent
  yells ``Cowabunga Dude!'' in the last action before moving forward into the
  cell that contains the wumpus and no pit.
  
  \vspace{.1in}
  \textbf{Task}

  Modify your wumpus agent to seek Nirvana.

  \begin{itemize}
    \item You will want to able to ask the knowledge base if Nirvana is 
      achievable in a given cell
      (yes wumpus, no pit).
    \item Add a method to the agent the checks if the cell that
      is forward of the agent is Nirvana achievable.  If it is,
      then remove any contents from the plan queue, and push
      a YELL action and a FORWARD action, then return true.
      If the forward cell is not Nirvana achievable, then
      do nothing and return false.
    \item Add to the if/else if chain in \texttt{ChooseAction()}
      after \texttt{if(gold > 0)} and before \texttt{else if(kb.AskGold(x,y))}
      an \texttt{else if} that calls your new method.  If it returns true,
      pop an action from the queue.
  \end{itemize}

  Run your agent with this enabled on at least 100 worlds with the nirvana option
  turned on in the server: \texttt{--nirvana 1}.  The server will reward the
  agent with 10000 points if Nirvana is obtained by yelling followed by being
  eaten.

  Save the server error and log files, and submit them to the Canvas task.
  Use git to push your code.

\end{problem}


